---
title: "Report"
author: "José Carlos Del Valle"
output: word_document
params:
  n: NA
---

```{r echo = FALSE}
# Variables globales para el código
db<-get(params$n)
p = params$n
Data2<-tibble::as_tibble(get(p))
    if(ncol(Data2)<3){
      Data2<-iris
    }
    DataN<-(Data2[,purrr::map_lgl(Data2,is.numeric)])
    
    corr <- round(cor(na.omit(DataN)), 1)
mlc<-corr[lower.tri(corr)]

A<-row.names(corr)
nomb<-c()
for(i in 1:(length(A)-1)){
  for(j in (i+1):(length(A))){
    nomb<-c(nomb,paste0(A[i]," & ",A[j]))
  }
}

Order<-data.frame(A=nomb,B=mlc)
Order<-Order[order(Order[[2]]),]

minR<-Order[(Order[[2]])< -.3,1]
maxR<-Order[(Order[[2]])>.3,1]
indR<-Order[abs(Order[[2]])<.3,1]

    
    pl1<-try(ggcorrplot::ggcorrplot(corr, hc.order = TRUE, 
                    type = "lower", 
                    lab = TRUE, 
                    lab_size = 3, 
                    method="circle", 
                    colors = c("tomato2", "white", "springgreen3"), 
                    title=paste0("Correlogram of ",p), 
                    ggtheme=theme_bw))

```

The ``r params$n`` data set has ``r ncol(db)`` variables named: ``r names(db)``.

We can see some relevant information in the following table:

```{r, echo=FALSE, fig.align="center"}
dfdesc<-round(describe(iris),3)
dfdesc<-dfdesc[,1:(ncol(dfdesc)-4)]
    kable(dfdesc)
```


The most correlated variabes are: ``r maxR``, therefore, we are able to predict or classify

The variables with inverse correlation are: ``r maxR``, therefore, we are able to predict or classify as well

Also, we can say that the following variables are independant of each other: ``r indR``.


```{r, echo=FALSE, fig.align="center"}
    pl1
```

We can see a scatter plot to confirm the previous plot, the more it looks like a line, the more there is a relationship between them


```{r, echo=FALSE, fig.align="center"}
  plot(DataN[,1:min(5,ncol(DataN))],col=rainbow(ncol(DataN)))
```

The distribution of each variable allows us to observe outlaiers and fit parametric models

```{r, echo=FALSE, fig.align="center"}
  all_nms<-names(Data2)
    all_N<-names(DataN)
    clasif<-all_nms[!all_nms %in% all_N]
    if(length(clasif)!=0){
    ntcls<-names(Data2) %in% clasif
    
    names(Data2)[ntcls]<-paste0("Cl",1:sum(ntcls))
    names(Data2)[!ntcls]<-paste0("Nm",1:sum(!ntcls))
    
    p <- ggplot(Data2, aes(factor(Cl1),Nm1))
    
    p + geom_violin() + geom_jitter(height = 0, width = 0.05) +  theme_minimal() +
        ylab((all_N)[1]) +
        xlab((clasif)[1])
    }else{
      names(Data2)<-paste0("Nm",1:ncol(Data2))
      Data2<-scale(Data2)
      DF2<-data.frame(Y=do.call(c,purrr::map(Data2,c)),
      X=rep(all_nms,each=nrow(Data2)))
      
      p <- ggplot(DF2, aes(factor(X),Y))
      p + geom_violin() + geom_jitter(height = 0, width = 0.05) +  theme_minimal() +
          ylab((all_N)[1])+xlab("Variables")
    }
```





